{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }

### 2017-09-20 Meetings/AUGrelated/mst1_tfm_200917.tex
update To the Tex file for MST1 TFM
Final version of TFM presentation 20 September

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> We have comparable edge density and divertor neutral
        pressure 
      \item<3|only@3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<3|only@3> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
        different current even though obtained at different values of $\Lambda_{div}$. 
      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
        $\Lambda_{div}$ without sensible difference among the current
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{H-Mode investigation: puffing location}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
    \centering{\includegraphics<2-3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item Similar puff from Lower and Upper divertor valves
        (\alert{we asked for divertor/midplane valves})
      \item<2-> Edge density profiles from Li-Beam evolution are
        pretty similar
      \item<3|alert@3> Similar behavior observed from RIC Antenna 4
        for the available shot
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Compare Similar fueling with/without cryopumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}}
    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOff}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> Same fueling but with cryo-pumps. Clearly different in
        terms of Edge density and Divertor pressure
      \item<2-> Also with this amount of fueling no instance of SOL
        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
      \item<3> Comparison of fluctuations during the plunge at higher
        density (\alert{ELM included}) reveal differences in
        fluctuations. \alert{ELM resolved measurement to be properly done}

@@

\begin{frame}{Matching scenarios with cryo-pumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
    %\centering{\includegraphics<3>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOffMatch}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> To match similar edge density and divertor pressure
        and to reach the same level of detachment we increase the
        fueling by almost a factor of 3, increasing also the rate. In
        addition to that we also increase substantially the N puffing
      \item<2-> Without cryopumps evidence of stronger SOL profile
        flattening from Li-Be. \alert{To be compared with appropriate
          variation of $\Lambda_{div}$}
      % \item<3> Clear difference in the shape of I$_s$ structure and in
      %   PDF although it is not yet \alert{ELM resolved}
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{What is missing}
  \Fontvi
  \begin{enumerate}
    \item RIC profiles with possible poloidal variation among the
      antennas in particular in H-Mode. \textcolor{red}{To be done}
    \item Li-Be ELM resolved profile variation with $\Lambda_{div}$
      \textcolor{red}{To be done}
    \item Li-Be fluctuations \textcolor{red}{To be done}
    \item Structures size and velocities in L-Mode
      \textcolor{orange}{In progress}
    \item Radiation front movement \textcolor{orange}{In progress}
    \item Can we have from stark-broadening the movement of density
      front towards the X-Point \textcolor{red}{To be done, maybe not
        feasible}
    \item Neutrals analysis from D$_{\alpha}$ camera
      \textcolor{orange}{In progress}
    \item Fast-camera \textcolor{red}{To be done}
    \item Other?
  \end{enumerate}
\end{frame}

\begin{frame}{2018}
  \textbf{Just a brainstorming exercise so far}
  \begin{itemize}
    \item X-point probe. Realistically there should be man-power for
      proper operation and we need information below the midplane
      before entering the divertor region
    \item NPH evaluation of Ti
    \item Parallel and perpendicular momentum variation at high
      density. We already know there is a change in the perpendicular
      flow to be complemented with parallel flow as well
    \item Divertor modification? I guess SP movement is not feasible
      in AUG but keeping the SP at the same position and moving the
      X-point (vertically/radially) can induce some modification?
    \item Increasing the density through pellet is feasible?
    \item Isotope effect? In case campaign is foreseen we could change
      parallel flow and recycling (?)
  \end{itemize}
\end{frame}
\end{document}

>>>>

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<3|only@3> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
        different current even though obtained at different values of $\Lambda_{div}$. 
      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
        $\Lambda_{div}$ without sensible difference among the current
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{H-Mode investigation: puffing location}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=0.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingLocation}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
    \only<3>{
      \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}
        \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
        \draw [->, ultra thick, white] (0.62, 0.45) -- (0.72, 0.55);
      \end{tikzonimage}   
    }
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> Similar puff from Lower and Upper divertor valves
        (\alert{we asked for divertor/midplane valves})
      \item<2-> Discharge with a total amount 6.5 heating power
        with equivalent behavior also in the lower divertor
        independently from the puffing location
      \item<3-> Edge density profiles from Li-Beam evolution are
        pretty similar
      \item<3|alert@3> Similar behavior observed from RIC Antenna 4
        for the available shot
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Compare Similar fueling with/without cryopumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
    \centering{\includegraphics<2>[height=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278}}
    \only<3>{
    \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}
      \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
      \draw [->, ultra thick, dashed, red] (0.62, 0.45) -- (0.72, 0.55);
    \end{tikzonimage}}
  \centering{\includegraphics<4>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOff}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
    \item<1-> Same fueling but with cryo-pumps
      \item<1-> H-5 density is different and remain constant, both
        divertor and midplane pressure are reduced (to 1/3
        approximately) no sign of detachment
      \item<2-> Different ELMy regimes reached with reduced size and
        increased frequency without the crypumps
      \item<3-> Also with this amount of fueling no instance of SOL
        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
      \item<4> Comparison of fluctuations during the plunge at higher
        density (\alert{ELM included}) reveal differences in
        fluctuations. \alert{ELM resolved measurement to be properly done}

@@

\begin{frame}{Matching scenarios with cryo-pumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34281}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
    4\centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOffMatch}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> To match similar edge density and divertor pressure
        and to reach the same level of detachment we increase the
        fueling by almost a factor of 3, increasing also the rate. In
        addition to that we also increase substantially the N
        puffing. \alert{Degraded H-Mode reached earlier in density
          without the cryopumps}
      \item<2-> Similar ELMy behavior obtained during the density ramp  
      \item<3-> Without cryopumps evidence of stronger SOL profile
        flattening from Li-Be. \alert{To be compared with appropriate
          variation of $\Lambda_{div}$}
       \item<4> The shape of the PDF is rather similar with closer
         values of autocorrelation time at similar values of divertor
         collisionality. \alert{Not yet ELM resolved}
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{What is missing}
  \Fontvi
  The analysis is still in progress and we are not ready yet to draw
  final conclusions. Among the future on going analysis we can list:
  \begin{enumerate}
    \item RIC profiles with possible poloidal variation among the
      antennas in particular in H-Mode. \textcolor{red}{To be done}
    \item Li-Be ELM resolved profile variation with $\Lambda_{div}$
      \textcolor{red}{To be done}
    \item Li-Be fluctuations \textcolor{red}{To be done}
    \item Structures size and velocities in L-Mode
      \textcolor{orange}{In progress}
    \item Radiation front movement \textcolor{orange}{In progress}
    \item Evolution of divertor profiles from Spectroscopy
      \textcolor{orange}{In progres}
    \item Neutrals analysis from D$_{\alpha}$ camera combined with
      KN1D code for evolution of neutrals
      \textcolor{orange}{In progress}
    \item Fast-camera \textcolor{red}{To be done}
  \end{enumerate}
\end{frame}

\end{document}
